\Large \bf Traffic Sign Classification

### 2017-12-19 paper/main.tex
Partial results for augmentation

@@

\begin{figure}
\includegraphics[width=3.25in]{accuracy}
\caption{Accuracy over 200 epochs. Data for ``test'' instances are taken from performance on a validation set at the end of each epoch}
\end{figure}

\begin{figure}
\includegraphics[width=3.25in]{loss}
\caption{Loss over 200 epochs. Data for ``test'' instances are taken from performance on a validation set at the end of each epoch}
\end{figure}

>>>>

\subsection{Training}

I trained the models over 200 epochs using the default batch size of 32 and a learning rate of 0.001. I used categorical cross-entropy as the loss function and stochastic gradient descent as the optimizer, which is suggested for multi-label classification problems \cite{lasagne_loss}.

@@

\begin{figure}
\includegraphics[width=3.25in]{accuracy}
\caption{Accuracy over 200 epochs on the base image set. Data for ``test'' instances are taken from performance on a validation set at the end of each epoch}
\end{figure}

\begin{figure}
\includegraphics[width=3.25in]{loss}
\caption{Loss over 200 epochs on the base image set. Data for ``test'' instances are taken from performance on a validation set at the end of each epoch}
\end{figure}

In order to assess the benefit of augmenting the data set with simple transformations of training images, I trained the model again on the same architecture, randomly applying a gaussian blur to half of the training examples. I observed a marginal improvement over the unaugmented data set, with the new model correctly classifying 96.00 \% of test images. Due to time limitations, it was not possible to experiment with other transformations, though I suspect that applying a random mix of transformations to generate the augmented data set would produce better results, since this technique has been used with considerable success in the past \cite{ciresan_committee_2011}. Figure 3 and Figure 4 show the accuracy and loss of the network over 200 training epochs when trained the augmented data set.

\begin{figure}
\includegraphics[width=3.25in]{accuracy}
\caption{Accuracy over 200 epochs using data augmentation. Data for ``test'' instances are taken from performance on a validation set at the end of each epoch}
\end{figure}

\begin{figure}
\includegraphics[width=3.25in]{loss}
\caption{Loss over 200 epochs using data augmentation. Data for ``test'' instances are taken from performance on a validation set at the end of each epoch}
\end{figure}
